Query Optimization for Dynamic Imputation

### 2017-05-12 paper/relatedwork.tex
paper: mark sections for sam to review

\todo{confirm that this reading of Yang is correct}
\cite{yang2015lenses} develops an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators, called Lenses. These can be used
to repair missing values by imposing data constraints such as \verb|NOT NULL|. 
Similarly to \ProjectName{}, they provide a way to balance between the quality of the cleaning 
performed (expressed by the confidence of their output) and the cost of those operations. However, their 
repairs take place on a per-tuple basis, with the non-deterministic layer of their system replacing place-holder
variables with inferred values. Meanwhile, \ProjectName{} optimizes imputation at the plan-level and
provides the same impute technique for all tuples streaming through a given operator.

@@

The planning algorithm that we present has similarities to the multi-objective query optimizer in~\cite{trummer2014}.
Both algorithms handle plans which have multiple cost functions by maintaining sets of Pareto optimal plans and pruning plans which become dominated.
In \ProjectName{}, costs are expected to grow monotonically as the size of the plan increases, which simplifies the optimization problem significantly.
\cite{trummer2014} handles the more complex case of cost functions which are piecewise linear, but not necessarily monotonic.

>>>>

\review{
\cite{yang2015lenses} develops an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators, called Lenses. These can be used
to repair missing values by imposing data constraints such as \texttt{NOT NULL}. 
Similarly to \ProjectName{}, they provide a way to balance between the quality of the cleaning 
performed (expressed by the confidence of their output) and the cost of those operations. However, their 
repairs take place on a per-tuple basis, with the non-deterministic layer of their system replacing place-holder
variables with inferred values. Meanwhile, \ProjectName{} optimizes imputation at the plan-level and
provides the same impute technique for all tuples streaming through a given operator.
}

@@

\review{
The planning algorithm that we present has similarities to the multi-objective query optimizer in~\cite{trummer2014}.
Both algorithms handle plans which have multiple cost functions by maintaining sets of Pareto optimal plans and pruning plans which become dominated.
In \ProjectName{}, costs are expected to grow monotonically as the size of the plan increases, which simplifies the optimization problem significantly.
\cite{trummer2014} handles the more complex case of cost functions which are piecewise linear, but not necessarily monotonic.
}
